Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
wordings intro

Modern implementations of embedded control have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with impact in numerous application areas such as environmental
control and robotics~\cite{astrom1997computer, Franklin15}.

@@

By contrast, we propose to leverage very recent step-change in \emph{program
synthesis}.  Program synthesis engines use a program specification as the
starting point, and subsequently generate a sequence of candidate programs. 
The candidate programs are iteratively refined to match the specification
more closely.  Program synthesisers that implement Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{sketch} are now able to generate programs
for highly non-trivial specifications with a very high degree of automation. 
Modern CEGIS engines implement combinations of automated testing, genetic
algorithms and SMT-based automated reasoning~\cite{DBLP:conf/lpar/DavidKL15,
DBLP:conf/cav/0001A14}.

@@

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour and the controller operates in both
discrete time and state-space.  The key insight of our approach is that the
problem can be translated into a \emph{single, joint domain}, which
represents a bi-simulation of the original, hybrid dynamics.  Given our
primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with fixed word
length (FWL).  We calculate the deterministic effect of the FWL and
quantization errors are included in the model as an additive uncertainty,
which is taken into account during the synthesis of the controller.

>>>>

Modern implementations of embedded control have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}.

@@

By contrast, we leverage very recent step-change in the scalability of
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs.  The candidate programs are iteratively refined to match
the specification more closely.  Program synthesisers that implement
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
able to generate programs for highly non-trivial specifications with a very
high degree of automation.  Modern CEGIS engines implement combinations of
automated testing, genetic algorithms and SMT-based automated
reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}.

@@

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour and the controller operates in both
discrete time and discrete state space.  The key insight of our approach is
that the problem can be translated into a \emph{single, joint domain}, which
represents a bi-simulation of the original, hybrid dynamics.  Given our
primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with fixed word
length (FWL).  We calculate the deterministic effect of the FWL and
quantization errors are included in the model as an additive uncertainty,
which is taken into account during the CEGIS-based synthesis of the
control software for the plant.
